Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-11-20 paper.tex
Removed previous bold text. Responded to all referee comments and have made adjustments to the paper. Still have a few questions and things to finish up leftover regarding the last comment.

The first generation of stars transformed a cold and dark universe 
by illuminating and enriching up their neighborhoods with radiation
and heavy elements. The formation of these first stars is a crucial step in the cosmological evolution of the universe because the metals and feedback they deliver to their local environments are necessary for further star production and chemical enrichment. Without these initial stars, heavier metals would not have been produced, and a different universe would be observed than what is observed today. These stars are, by definition, metal-free (Population III; Pop III) and are \textbf{traditionally} thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}\textbf{, although more recent work has shown that lower mass ($M < 1 M_{\odot}$) Pop III stars can be formed \citep{Greif11_P3Cluster, Clark11_Frag, Stacy11}.} A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}. The supernova will spread the enriched guts of the Pop III star out across its local environment, providing the area with elements the universe has not yet seen.

@@

Diffuse gas is optically thin to LW radiation, thus a background builds over time and can suppress \hh{} formation, delaying Pop III star formation. Furthermore, nearby sources of LW radiation can boost the intensity above the background value which facilitates further \hh{} dissociation in minihalos. This process can be counteracted with a sufficient amount of \hh{} already present within a halo, via \hh{} self-shielding. Halos with an \hh{} column density of N$_{\rm H2}$ $\geq$ 10$^{14}$ cm$^{-2}$ can suppress the photodissociation of \hh{} by LW photons \citep{Draine96}, giving the halo a chance to form Pop III stars. Other sources of the suppression of Pop III star formation are streaming baryonic velocities \citep{Tselia11, Greif11_Delay, Naoz12,OLeary12}, arising from recombination, and dynamical heating, occurring during the virialization of halos \citep{Yoshida03, Fernandez14}. \textbf{X-ray heating from high-mass X-ray binaries also has the potential to suppress Pop III star formation \citep{Jeon14}.}

@@

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter paticle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc.  \textbf{We refine the cells when one of the following criteria are met: (1) the baryon or dark matter overdensity exceeds $3\bar{\rho}_{\rm b,DM} \times 2^{\ell(3+\epsilon)}$, or (2) the local Jeans length is less than eight cell widths.  Here $\rho_{\rm b,DM}$ is the baryon or dark matter cosmic mean density, $\ell$ is the AMR level, and $\epsilon = -0.2$ invokes super-Lagrangian refinement behavior.} The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions. \textbf{We note that this initialization redshift is too low, even with 2nd order Lagrangian perturbation theory, for a small cosmological volume and results in delayed structure formation at very high redshift $z > 20$.} The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39. \textbf{Throughout the rest of the paper, all numbers are in physical units, unless otherwise specified.}

@@

	\item molecular hydrogen \textbf{number} fraction, f$_{\rm H2}$ > 10$^{-3}$
\end{enumerate}
\textbf{The critical metallicity marks where dust cooling becomes efficient enough to cause fragmentation at high densities \citep[e.g.][]{Schneider06_Frag}.  In practice, we find about 10 per cent of Pop III star particles having a non-zero metallicity below this value.  This scenario occurs when a halo is externally enriched by a nearby supernova.  Because of uncertainties with turbulent mixing and collapse timescales, we choose not to predict the final metallicity at zero-age main sequence and assign the star particle the metallicity of the densest cell.  The chosen threshold density are consistent with values found in previous simulations of Pop III star formation \citep[e.g.][]{Hirano15} at our resolution limit.  Additionally, it is similar to a density that would trigger another mesh refinement past level 12.  At these scales, Jeans length refinement is the most common because of the cold temperatures in the cloud core.  The molecular hydrogen criterion is also consistent with previous work in the ``loitering'' phase of molecule formation between $10^2$ and $10^8 \cubecm$ before three-body reactions become important \citep[e.g.][]{Omukai10}.}

If within \textbf{10} pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells. \textbf{In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance. We found that even when this number was decreased to 0.065 pc, the number of star particles that formed was unchanged.  Our density threshold for star particle formation is equivalent to a molecular core.  Fragmentation of metal-free gas into massive stellar precursors can occur at scales down to 1000~AU \citep[e.g.][]{Turk09, Stacy11} with molecular cores, therefore our results on multiplicity should be considered as lower limits.}

@@

We use the mass-dependent hydrogen ionizing and LW luminosities and lifetimes from \citet{Schaerer02} and a mass-independent photon energy of E$_{\rm ph}$ = 29.6 eV, which is appropriate for the nearly mass-independent surface temperature of Pop III stars, at 10$^{5}$ K. A Type II supernova results if the Pop III star dies with a mass between 11 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40. A pair instability supernova (PISNe) results if the star dies with a mass between 140 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 260. Outside of these mass ranges, the Pop III star dies as a black hole. In this simulation, no black hole physics are implemented, so the Pop III star simply turns into an inert collisionless particle. When 11 $\leq$ M$_{\star}$/M$_{\odot}$ < 20, the star dies as a normal Type II supernova with an energy of 10$^{51}$ erg. From 20 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40, the star dies as a hypernova with energies taken from \citet{Nomoto06}. The PISNe have explosion energies from \citet{2002ApJ...567..532H}, of which the analytic function fit to their models can be seen in Eq. 12 of W12. \textbf{With our chosen IMF (Eq. \ref{IMF}), 59, 36, and 5 per cent of Pop III stars produce Type II SN, black holes with no SN, and PISNe, respectively.}

@@

Upon numerically calculating the shielding factor of \hh{} for simulated protogalaxies, Wolcott-Green et al. determined that a slight adjustment to the shielding factor from \citet{Draine96} is sufficient to account for inaccuracies at higher temperatures. The implemented shielding factor is then (see Eq. 10 in \citet{Wolcott11}):
\begin{equation} \label{shield}
	\begin{multlined}
	f_{\rm sh}(N_{\rm H2}, T) = \frac{0.965}{(1+x/b_{5})^{1.1}} + \frac{0.035}{(1+x)^{0.5}}  \times \\ \exp [-8.5 \times 10^{-4} (1+x)^{0.5}]
	\end{multlined}
\end{equation}
Here, x $\equiv$ N$_{\rm H2}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter. This shielding factor acts as a multiplier to the \hh{} dissociation rate, where if the shielding factor equals one, there is no shielding, and zero if there is maximum shielding. \textbf{\citet{Hartwig15} use the same shielding factor equation from \citet{Wolcott11} but implement an improved calculation of the column density to incorporate the relative gas velocities and geometries of the halo. This method takes into account the Doppler-shifting of spectral lines, which can affect \hh{} shielding. With the improved calculation of the column density, they find that the shielding factor is larger for gas at higher temperatures near $10^4$~K than when the shielding factor is calculated for an average column density for the halo, meaning that self-shielding is generally less efficient for higher temperatures. In this work, we do not take into account the Doppler-shifting of spectral lines, but as will be seen below, our halos are less massive and contain gas at lower temperatures. Our calculation of the shielding factor is still valid for the temperature range of our halos, and therefore, the Doppler-shifting of spectral lines is not expected to affect our results.}

@@

For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, redshift\textbf{, and for a given \hh{} fraction halo profile}. Figure \ref{fig:shield_mass} shows the shielding factor as a function of halo mass, for redshifts $z = 9$, $15$, and $25$ in red, blue and black, respectively. The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$. \textbf{To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at z = 24.1 from \citet{OShea08} (their Figure 13d) with $J_{21}$ = 0, which was extracted directly from their plot. These profiles were approximated with a piecewise power-law for simplicity. As the halo masses increase, the shielding factor increases, meaning there is less shielding occurring within that halo. This behavior occurs because at larger radii, there is less \hh{} available, and therefore, the effects of shielding are decreased.} Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s. At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum. The shielding factor will then significantly decrease the dissociation rate of \hh{}, allowing for the presence of \hh{} within a LW background. Smaller mass halos can then form Pop III stars since \hh{} will survive in the halo for a longer amount of time. We also see that for column densities at just under $10^{17} \rm cm^{-2}$, the shielding factor quickly drops to 0.1 for a halo with this particular circular velocity, showing that \hh{} shielding can affect the dissociation rate of \hh{} in relatively low halo masses.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/shield_mass.pdf}
    \caption{Shielding factor as a function of halo mass. Solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines indicate a core radius of $f_{c} = 10^{-4}$. For these parameters, assuming the Doppler broadening parameter equals the circular velocity, \textbf{and assuming \hh{} fraction halo profiles from \citet{oshea07a}, }the shielding factor is below 1 percent. The green line shows the shielding factor as a function of \hh{} column density for a circular velocity of 10 km/s. \textbf{Note that a shielding factor of 1 (0) corresponds to no (complete) shielding.}}
    \label{fig:shield_mass}
\end{figure}
%====================================================================
\section{Results}
%====================================================================
In this section, we will present the distribution of host halo masses of Pop III stars, the relation between the mass distribution and the LW background radiation, and the distribution of various Pop III properties.

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z = 9.3$. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles. After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box. \textbf{When the first Pop III star forms in our simulation at $z = 27$, there are only 6 halos that are above $10^5~\Ms$, which are resolved by 50 DM particles, consistent with analytical expectations from an ellipsoidal variant of Press-Schechter formalism \citep{PS74,Sheth01}.} These \textbf{Pop III} stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings. Metal-enriched star formation begins to take place as soon as enough metals are present within a halo. In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place. By the end of the simulation, 20\% of the box has an ionized fraction greater than 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity \textbf{coming from sources} as a function of time, \textbf{the LW background given by equation \ref{LWbg} in units of J$_{21}$,} and temperature projections of the box at certain points in time.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/hmf.pdf}
    \caption{Halo mass function of the last output of the simulation at $z$ = 9.3. The thick, black line is the analytic Sheth-Tormen mass function. The distribution of halo masses matches well with analytical expectations above 10$^{5}$ M$_{\odot}$, where halos are captured by 50 particles. \textbf{The vertical blue line indicates our halo mass resolution limit of 10$^{5}$ M$_{\odot}$.}}
    \label{fig:hmf}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{images/jlw_xe_bg_mass_weight.pdf}
    \caption{For the entire box, the average mass weighted LW background \textbf{from sources} shown in solid red and the fraction of the volume ionized above 10\% versus time shown in solid black. \textbf{The red dashed line represents the LW background implemented in the simulation (see Equation \ref{LWbg}). The solid red line in the legend refers to both the solid and dashed lines in the figure.}Temperature projections are shown at the points indicated by the arrows.}
    \label{fig:JLW_xe_mass}
\end{figure}

@@

%====================================================================
\subsection{Population III host halo masses}
%====================================================================
 To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}, \textbf{an algorithm that adaptively refines halos found with a friends-of-friends method in position and velocity phase-space and also temporally.} The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$. The total mass is subsequently used in our analysis. \textbf{For stars that form in subhalos identified by \rockstar{}, we assign the parent halo mass as the host halo mass.  There is one interesting case that we exclude from our analysis, where the parent halo is above the atomic cooling limit, because the radiative cooling physics are different in this regime and is not sensitive to a LW background.  Here seven Pop III stars form in a pristine $10^6 \msun$ subhalo inside of a $3 \times 10^8 \msun$ atomic cooling parent halo.  Because this object only contains 1 per cent of the number of Pop III stars, it only affects our average halo masses by a similar amount.} We also take the center and virial radius from the \rockstar{} halo catalog. \textbf{About 1\%} of Pop III stars do not form in a halo identified by \rockstar{}. Assuming that Pop III stars must form in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data by determining the sphere that contains an average overdensity of 200 $\rho_{\rm c}$. We calculate the LW intensity impinging on each halo by summing up the contribution coming from each radiating star particle outside the virial radius of the host halo. This is then added to the constant LW background implemented in the simulation (Eq. \ref{LWbg}). In this work, we only analyze halos below the atomic cooling limit.

@@

%====================================================================
\subsection{Variations in the halo masses at collapse}
\label{sec:variations}
%====================================================================
Previous studies have focused on the minimum halo mass of Pop III hosts as a function of LW intensity. However, they have also found that Pop III stars often form in halos up to an order of magnitude greater than the minimum. We also have found that Pop III star formation occurs in a similar range of host halo masses throughout our simulation. There are three main causes of this significant variation in mass. First \textbf{given our assumed IMF (Equation \ref{IMF}), 36 per cent} of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.  Second-generation stars forming later in that halo could still be metal-free if no external enrichment occurs. Thus they would form in halos substantially larger than the minimum, as it takes tens of millions of years for the halo to recover its gas after radiative feedback \citep{Muratov13, Jeon14_Recovery}.  Second, dynamical heating from mergers and accretion provide a heating source inside the growing halo, preventing the gas from efficiently cooling via \hh{}. This turbulent stirring can delay star formation that could cool through \hh{} in an ideal situation but otherwise forms in halos more massive than the minimum \citep{Yoshida03, Wise19}. Finally, temporal fluctuations in the local LW radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool. While this may only be a small effect in some halos where the local LW radiation fluctuations are relatively small and star formation is distant, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active star formation sites.  In summary, the timing of Pop III star formation depends on both local -- halo histories of star formation and growth -- and environmental properties.  The combination of these three processes determines which halos will be able to form Pop III stars, and thus results in a wide range of host halo masses.

@@

\begin{itemize}
	\item We find that Pop III stars are forming in halos with a mean mass below $10^{6}$ M$_{\odot}$, which falls well below the M01 relation, until $z=15$, at which point the mean halo mass rises above the M01 relation to a mean value of $3 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive galaxy in the simulation box.
	\item \hh{} self-shielding allows halos below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.  Self-shielding creates a disconnect between the \textbf{instantaneous}LW background and the collapse, resulting in a broad mass distribution of metal-free star forming halos and no strict correlation between the two quantities.
	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.
	\item By the end of the simulation, halos with masses $>10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass halos, resulting in galaxies with young and old metal-free stars. 
\end{itemize}

>>>>

The first generation of stars transformed a cold and dark universe 
by illuminating and enriching up their neighborhoods with radiation
and heavy elements. The formation of these first stars is a crucial step in the cosmological evolution of the universe because the metals and feedback they deliver to their local environments are necessary for further star production and chemical enrichment. Without these initial stars, heavier metals would not have been produced, and a different universe would be observed than what is observed today. These stars are, by definition, metal-free (Population III; Pop III) and are traditionally thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}, although more recent work has shown that lower mass ($M < 1 M_{\odot}$) Pop III stars can be formed \citep{Greif11_P3Cluster, Clark11_Frag, Stacy11}. A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}. The supernova will spread the enriched guts of the Pop III star out across its local environment, providing the area with elements the universe has not yet seen.

@@

Diffuse gas is optically thin to LW radiation, thus a background builds over time and can suppress \hh{} formation, delaying Pop III star formation. Furthermore, nearby sources of LW radiation can boost the intensity above the background value which facilitates further \hh{} dissociation in minihalos. This process can be counteracted with a sufficient amount of \hh{} already present within a halo, via \hh{} self-shielding. Halos with an \hh{} column density of N$_{\rm H2}$ $\geq$ 10$^{14}$ cm$^{-2}$ can suppress the photodissociation of \hh{} by LW photons \citep{Draine96}, giving the halo a chance to form Pop III stars. Other sources of the suppression of Pop III star formation are streaming baryonic velocities \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12, Schauer19,Hirano17_Science}, arising from recombination, and dynamical heating, occurring during the virialization of halos \citep{Yoshida03, Fernandez14}. X-ray heating from high-mass X-ray binaries also has the potential to suppress Pop III star formation \citep{Jeon14}.

@@

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter paticle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc.  \textbf{We refine the cells when one of the following criteria are met: (1) the baryon or dark matter overdensity exceeds $3\bar{\rho}_{\rm b,DM} \times 2^{\ell(3+\epsilon)}$, or (2) the local Jeans length is less than eight cell widths.  Here $\rho_{\rm b,DM}$ is the baryon or dark matter cosmic mean density, $\ell$ is the AMR level, and $\epsilon = -0.2$ invokes super-Lagrangian refinement behavior.} The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions. \textbf{We note that this initialization redshift is too low, even with 2nd order Lagrangian perturbation theory, for a small cosmological volume and results in delayed structure formation at very high redshift $z > 20$.} The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39. Throughout the rest of the paper, all numbers are in physical units\textbf{, unless otherwise specified}.

@@

	\item molecular hydrogen number fraction, f$_{\rm H2}$ > 10$^{-3}$
\end{enumerate}
The critical metallicity marks where dust cooling becomes efficient enough to cause fragmentation at high densities \citep[e.g.][]{Schneider06_Frag}.  In practice, we find about 10 per cent of Pop III star particles having a non-zero metallicity below this value.  This scenario occurs when a halo is externally enriched by a nearby supernova.  Because of uncertainties with turbulent mixing and collapse timescales, we choose not to predict the final metallicity at zero-age main sequence and assign the star particle the metallicity of the densest cell.  The chosen threshold density are consistent with values found in previous simulations of Pop III star formation \citep[e.g.][]{Hirano15} at our resolution limit.  Additionally, it is similar to a density that would trigger another mesh refinement past level 12.  At these scales, Jeans length refinement is the most common because of the cold temperatures in the cloud core.  The molecular hydrogen criterion is also consistent with previous work in the ``loitering'' phase of molecule formation between $10^2$ and $10^8 \cubecm$ before three-body reactions become important \citep[e.g.][]{Omukai10}.

If within \textbf{10} pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells. In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance. \textbf{We found that even when this number was decreased to 0.065 pc, the number of star particles that formed was unchanged.  Our density threshold for star particle formation is equivalent to a molecular core.  Fragmentation of metal-free gas into massive stellar precursors can occur at scales down to 1000~AU \citep[e.g.][]{Turk09, Stacy11} with molecular cores, therefore our results on multiplicity should be considered as lower limits.}

@@

We use the mass-dependent hydrogen ionizing and LW luminosities and lifetimes from \citet{Schaerer02} and a mass-independent photon energy of E$_{\rm ph}$ = 29.6 eV, which is appropriate for the nearly mass-independent surface temperature of Pop III stars, at 10$^{5}$ K. A Type II supernova results if the Pop III star dies with a mass between 11 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40. A pair instability supernova (PISNe) results if the star dies with a mass between 140 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 260. Outside of these mass ranges, the Pop III star dies as a black hole. In this simulation, no black hole physics are implemented, so the Pop III star simply turns into an inert collisionless particle. When 11 $\leq$ M$_{\star}$/M$_{\odot}$ < 20, the star dies as a normal Type II supernova with an energy of 10$^{51}$ erg. From 20 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40, the star dies as a hypernova with energies taken from \citet{Nomoto06}. The PISNe have explosion energies from \citet{2002ApJ...567..532H}, of which the analytic function fit to their models can be seen in Eq. 12 of W12. With our chosen IMF (Eq. \ref{IMF}), 59, 36, and 5 per cent of Pop III stars produce Type II SN, black holes with no SN, and PISNe, respectively.

@@

Upon numerically calculating the shielding factor of \hh{} for simulated protogalaxies, Wolcott-Green et al. determined that a slight adjustment to the shielding factor from \citet{Draine96} is sufficient to account for inaccuracies at higher temperatures. The implemented shielding factor is then (see Eq. 10 in \citet{Wolcott11}):
\begin{equation} \label{shield}
	\begin{multlined}
	f_{\rm sh}(N_{\rm H2}, T) = \frac{0.965}{(1+x/b_{5})^{1.1}} + \frac{0.035}{(1+x)^{0.5}}  \times \\ \exp [-8.5 \times 10^{-4} (1+x)^{0.5}]
	\end{multlined}
\end{equation}
Here, x $\equiv$ N$_{\rm H2}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter. This shielding factor acts as a multiplier to the \hh{} dissociation rate, where if the shielding factor equals one, there is no shielding, and zero if there is maximum shielding. \citet{Hartwig15} use the same shielding factor equation from \citet{Wolcott11} but implement an improved calculation of the column density to incorporate the relative gas velocities and geometries of the halo. This method takes into account the Doppler-shifting of spectral lines, which can affect \hh{} shielding. With the improved calculation of the column density, they find that the shielding factor is larger for gas at higher temperatures near $10^4$~K than when the shielding factor is calculated for an average column density for the halo, meaning that self-shielding is generally less efficient for higher temperatures. In this work, we do not take into account the Doppler-shifting of spectral lines, but as will be seen below, our halos are less massive and contain gas at lower temperatures. Our calculation of the shielding factor is still valid for the temperature range of our halos, and therefore, the Doppler-shifting of spectral lines is not expected to affect our results.

@@

For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, redshift, and for a given \hh{} fraction halo profile. Figure \ref{fig:shield_mass} shows the shielding factor as a function of halo mass, for redshifts $z = 9$, $15$, and $25$ in red, blue and black, respectively. The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$. To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at z = 24.1 from \citet{OShea08} (their Figure 13d) with $J_{21}$ = 0, which was extracted directly from their plot. These profiles were approximated with a piecewise power-law for simplicity \textbf{given by Equation \ref{h2fitting}}. 
\begin{equation} \label{h2fitting}
	log_{10}(f_{\rm H2}) = -0.482 \times log_{10}(R_{\rm vir}) - 4.714
\end{equation}
As the halo masses increase, the shielding factor increases, meaning there is less shielding occurring within that halo. This behavior occurs because at larger radii, there is less \hh{} available, and therefore, the effects of shielding are decreased. Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s. At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum. The shielding factor will then significantly decrease the dissociation rate of \hh{}, allowing for the presence of \hh{} within a LW background. Smaller mass halos can then form Pop III stars since \hh{} will survive in the halo for a longer amount of time. We also see that for column densities at just under $10^{17} \rm cm^{-2}$, the shielding factor quickly drops to 0.1 for a halo with this particular circular velocity, showing that \hh{} shielding can affect the dissociation rate of \hh{} in relatively low halo masses.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/shield_mass.pdf}
    \caption{Shielding factor as a function of halo mass. Solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines indicate a core radius of $f_{c} = 10^{-4}$. For these parameters, assuming the Doppler broadening parameter equals the circular velocity, and assuming \hh{} fraction halo profiles from \citet{oshea07a}, the shielding factor is below 1 percent. The green line shows the shielding factor as a function of \hh{} column density for a circular velocity of 10 km/s. Note that a shielding factor of 1 (0) corresponds to no (complete) shielding.}
    \label{fig:shield_mass}
\end{figure}
%====================================================================
\section{Results}
%====================================================================
In this section, we will present the distribution of host halo masses of Pop III stars, the relation between the mass distribution and the LW background radiation, and the distribution of various Pop III properties.

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z = 9.3$. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles. After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box. When the first Pop III star forms in our simulation at $z = 27$, there are only 6 halos that are above $10^5~\Ms$, which are resolved by 50 DM particles, consistent with analytical expectations from an ellipsoidal variant of Press-Schechter formalism \citep{PS74,Sheth01}. These Pop III stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings. Metal-enriched star formation begins to take place as soon as enough metals are present within a halo. In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place. By the end of the simulation, 20\% of the box has an ionized fraction greater than 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity \textbf{coming from sources} as a function of time, \textbf{the LW background given by equation \ref{LWbg} in units of J$_{21}$,} and temperature projections of the box at certain points in time.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/hmf.pdf}
    \caption{Halo mass function of the last output of the simulation at $z$ = 9.3. The thick, black line is the analytic Sheth-Tormen mass function. The distribution of halo masses matches well with analytical expectations above 10$^{5}$ M$_{\odot}$, where halos are captured by 50 particles. The vertical blue line indicates our halo mass resolution limit of 10$^{5}$ M$_{\odot}$.}
    \label{fig:hmf}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{images/jlw_xe_bg_mass_weight.pdf}
    \caption{For the entire box, the average mass weighted LW background from sources shown in solid red and the fraction of the volume ionized above 10\% versus time shown in solid black. The red dashed line represents the LW background implemented in the simulation (see Equation \ref{LWbg}). \textbf{The solid red line in the legend refers to both the solid and dashed lines in the figure.}Temperature projections are shown at the points indicated by the arrows.}
    \label{fig:JLW_xe_mass}
\end{figure}

@@

%====================================================================
\subsection{Population III host halo masses}
%====================================================================
 To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}, an algorithm that adaptively refines halos found with a friends-of-friends method in position and velocity phase-space and also temporally. The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$. The total mass is subsequently used in our analysis. For stars that form in subhalos identified by \rockstar{}, we assign the parent halo mass as the host halo mass.  There is one interesting case that we exclude from our analysis, where the parent halo is above the atomic cooling limit, because the radiative cooling physics are different in this regime and is not sensitive to a LW background.  Here seven Pop III stars form in a pristine $10^6 \msun$ subhalo inside of a $3 \times 10^8 \msun$ atomic cooling parent halo.  Because this object only contains 1 per cent of the number of Pop III stars, it only affects our average halo masses by a similar amount. We also take the center and virial radius from the \rockstar{} halo catalog. About 1\% of Pop III stars do not form in a halo identified by \rockstar{}. Assuming that Pop III stars must form in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data by determining the sphere that contains an average overdensity of 200 $\rho_{\rm c}$. We calculate the LW intensity impinging on each halo by summing up the contribution coming from each radiating star particle outside the virial radius of the host halo. This is then added to the constant LW background implemented in the simulation (Eq. \ref{LWbg}). In this work, we only analyze halos below the atomic cooling limit.

@@

%====================================================================
\subsection{Variations in the halo masses at collapse}
\label{sec:variations}
%====================================================================
Previous studies have focused on the minimum halo mass of Pop III hosts as a function of LW intensity. However, they have also found that Pop III stars often form in halos up to an order of magnitude greater than the minimum. We also have found that Pop III star formation occurs in a similar range of host halo masses throughout our simulation. There are three main causes of this significant variation in mass. First given our assumed IMF (Equation \ref{IMF}), 36 per cent of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.  Second-generation stars forming later in that halo could still be metal-free if no external enrichment occurs. Thus they would form in halos substantially larger than the minimum, as it takes tens of millions of years for the halo to recover its gas after radiative feedback \citep{Muratov13, Jeon14_Recovery}.  Second, dynamical heating from mergers and accretion provide a heating source inside the growing halo, preventing the gas from efficiently cooling via \hh{}. This turbulent stirring can delay star formation that could cool through \hh{} in an ideal situation but otherwise forms in halos more massive than the minimum \citep{Yoshida03, Wise19}. Finally, temporal fluctuations in the local LW radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool. While this may only be a small effect in some halos where the local LW radiation fluctuations are relatively small and star formation is distant, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active star formation sites.  In summary, the timing of Pop III star formation depends on both local -- halo histories of star formation and growth -- and environmental properties.  The combination of these three processes determines which halos will be able to form Pop III stars, and thus results in a wide range of host halo masses.

@@

\begin{itemize}
	\item We find that Pop III stars are forming in halos with a mean mass below $10^{6}$ M$_{\odot}$, which falls well below the M01 relation, until $z=15$, at which point the mean halo mass rises above the M01 relation to a mean value of $3 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive galaxy in the simulation box.
	\item \hh{} self-shielding allows halos below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.  Self-shielding creates a disconnect between the \textbf{instantaneous} LW background and the collapse, resulting in a broad mass distribution of metal-free star forming halos and no strict correlation between the two quantities.
	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.
	\item By the end of the simulation, halos with masses $>10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass halos, resulting in galaxies with young and old metal-free stars. 
\end{itemize}
